---
title: "Homework 3"
author: Tu  Nguyen
output: github_document
---

This is my solution to HW2.


```{r setup, include = FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 2

Tidy data into "minute of the day" and "activity count" columns

```{r}
accel_df = 
  read_csv("./data/accel_data.csv") %>% 
   pivot_longer(
    activity.1:activity.1440,
    names_to = "minute",
    names_prefix = "activity.",
    values_to = "activity_count"
  ) %>% 
  mutate(
    weekday_or_weekend =
      recode(day,
             "Monday" = "weekday",
             "Tuesday" = "weekday",
             "Wednesday" = "weekday",
             "Thursday" = "weekday",
             "Friday" = "weekday",
             "Saturday" = "weekend",
             "Sunday" = "weekend")
  )

accel_df$day = factor(accel_df$day, levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))
accel_df[order(accel_df$day), ]
```

There are 6 variables which include `week`, `day_id`, `day`, `minute of the day`, `activity_count`, and `weekday_or_weekend`. There are total 50,400 observations. 


```{r}
accel_df_tidy = 
  accel_df %>% 
  group_by(week,day_id, day) %>% 
  summarise(
    mean_activity_count = mean(activity_count, na.rm = TRUE)
  )

accel_df_tidy$day = factor(accel_df_tidy$day, levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))
accel_df_tidy[order(accel_df_tidy$day), ]

accel_df_tidy %>% 
  pivot_wider(
    names_from = day,
    values_from = mean_activity_count
  )
```

Patient's activity count is high on the weekends during the first 3 weeks. In general, patient is more active during the weekdays. 

```{r}
ggplot(accel_df_tidy, aes(x = day_id, y = mean_activity_count, color = day)) + 
  geom_point() +
  geom_line()
```

From the graph, patient's activity counts decreased on Saturdays and Sundays from day 24 to day 31. 
Activity count of Fridays decreased from day 1 to day 22 but increased afterwards. On Tuesdays, Thursdays,and Friday, activity counts remained around the same pace. 



## Problem 3

Load the dataset

```{r}
devtools::install_github("p8105/p8105.datasets")
library(p8105.datasets)
data("ny_noaa")
```

Data cleaning (separate date, convert prcp to the same unit as snowfall, convert tmax and tmin to degree C)

```{r}
ny_noaa_df = 
  ny_noaa %>% 
  separate(date, into = c("year", "month", "day"), sep = "-")
```

```{r}
ny_noaa_df$tmin = as.double(as.character(ny_noaa_df$tmin))
ny_noaa_df$tmax = as.double(as.character(ny_noaa_df$tmax))

ny_noaa_df %>% 
  mutate(
    prcp = prcp * 10,
    tmin = tmin * 10,
    tmax = tmax * 10
  )
```

Most observed values in snowfall

```{r}
most_snow = table(ny_noaa_df$snow)
most_snow[most_snow == max(most_snow)]
```
The most observed values in snowfall is 0, which occurs 2008508 times. Because snow occurs mostly from December to March but for only certain days. 



